Bandwidth-Aware Reconfigurable Memory Design with Hybrid Memory Technologies

### 2011-04-10 paper.tex

Figure~\ref{fig:hw-config} shows an overview of BAROM hardware configuration.
The CMP system consists of multiple cores, where L1 cahces are private to each
core and lower level caches are shared by the cores. With the provided bandwidth
vs. capacity curves of various memory technologies that are obtained using the
method described in section~\ref{sec:tech-explore}, we can design a hybrid
on-chip memory system to always provide the highest bandwith. In order to
achieve this goal, we configure the memory hierarchy in the following
manner.\vspace{5pt}

@@

\noindent{}{\bf{Capacity of each level.}} The maximum availabe capacity of each
level is determined by the cross point of two memory technologies. In our case,
the capacities of SRAM/L2, STT-RAM/L2, and RRAM/L4 are 2MB, 512MB, and 1GB
respectively. Each level of memory if further configured to be multiple banks
the same way as the conventional cache design. At the system initialization, the
capacity of each level is defined to be the maximum available capacity of the
level. According to the reqirement of different applications, the capacities can
be reconfigured at run-time to provide best performance. The memory space of
each level can be reconfigured to form an internal level as shown in
Figure~\ref{fig:hw-config}. The hardware and software supports for
reconfiguration will be presented in the following sections.\vspace{5pt}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=2.5in]{figures/overview}
\caption{Overview of BAROM hardware configuration.}
\label{fig:overview}
\end{figure}

Figure~\ref{fig:overview} shows an overview of BAROM hardware configuration.
The CMP system consists of multiple cores, where L1 cahces are private to each
core and lower level caches are shared by the cores. With the provided bandwidth
vs. capacity curves of various memory technologies that are obtained using the
method described in section~\ref{sec:tech-explore}, we can design a hybrid
on-chip memory system to always provide the highest bandwith. In order to
achieve this goal, we configure the memory hierarchy in the following
manner.\vspace{5pt}

@@

\noindent{}{\bf{Capacity of each level.}} The maximum availabe capacity of each
level is determined by the cross point of two memory technologies. In our case,
the capacities of SRAM/L2, STT-RAM/L2, and RRAM/L4 are 2MB, 512MB, and 1GB
respectively. Each level of memory if further configured to be multiple banks
the same way as the conventional cache design. At the system initialization, the
capacity of each level is defined to be the maximum available capacity of the
level. According to the reqirement of different applications, the capacities can
be reconfigured at run-time to provide best performance. The memory space of
each level can be reconfigured to form an internal level as shown in
Figure~\ref{fig:overview}. The hardware and software supports for
reconfiguration will be presented in the following sections.\vspace{5pt}
